---
title: "2021-June-12"
author: "shao"
date: "6/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
tuesdata <- tidytuesdayR::tt_load(2021, week = 25)

tweets <- tuesdata$tweets
```
你可以使用以下两种方式提取关键词
# str_match(tweets$text, ">(.+?)</a>")[,2]
# str_replace(tweets$text, ".*?>(.+?)</a>.*?","\\1") %>% unique()


```{r}
info <- tibble::tribble(
        ~variable,      ~class,                  ~description,
       "datetime",    "double",      "Date and time of tweet",
        "content", "character",              "Text for tweet",
  "retweet_count",    "double",     "Retweet count for tweet",
     "like_count",    "double",        "Like count for tweet",
    "quote_count",    "double", "Quote tweet count for tweet",
           "text", "character", "Where tweet was posted from",
       "username", "character",         "Username of Tweeter",
       "location", "character",       "Location tweeted from",
      "followers",    "double",    "Followers of the tweeter",
            "url", "character",      "Canonical url of tweet",
       "verified",   "logical",           "Is user verified?",
            "lat",    "double",            "Latitude of user",
           "long",    "double",           "Longitude of user"
  )
```

```{r}
tweets_washed <- tweets %>% 
  mutate(platform = str_replace(tweets$text, ".*?>(.+?)</a>.*?","\\1")) %>% 
  select(-url, -text)
```


```{r}
tweets_washed <- tweets_washed %>% 
  mutate(lat = ifelse(location  == 'iPhone: 34.704040,-86.722909',34.704040,lat),
         long = ifelse(location  == 'iPhone: 34.704040,-86.722909',-86.722909,long))

```

iPhone: 34.704040,-86.722909 = madison alabama
he/they	= Chalmazel, France
At the home office = Gaithersburg, Maryland
Forde-Obama Hall = New York
Worldwide = Manchester, England
Kevin.Elder@GCSU.edu = Milledgeville, Georgia
World = Dubayy, United Arab
God's earth = Beijing
OAK / NYC / ATL / The World = NA
SP = La Spezia, Italy
Lil’ Rudyshire = NA

```{r}
library(geonames)
options(geonamesUsername="barnett874")

findcountry(25.252889, 55.17696777)
findcountry(40.712728, -74.00601520)
findcountry <- function(lat,long){
  if(round(lat,2) == 25.25 & round(long,2) == 55.18){return("United Arab")}else{
    country = GNcountryCode(lat,long)$countryName; return(country)
  }
}
round(55.17696777,2)
geo_country <- geo %>% 
  mutate(country = purrr::map2_chr(lat,long, ~findcountry(.x,.y)))

# 25.252889	55.17696777	<NULL>	

geo_country <- geo_country %>% 
  unnest(country) %>% 
  mutate(lat = as.double(lat),
         long = as.double(long))

tweets_washed <- left_join(tweets_washed,geo_country,by = c('lat','long'))
at_name <- tweets_washed$content %>% 
  str_split(pattern = ' ') %>% 
  unlist() %>% 
  str_extract('@.*') %>% 
  na.omit() %>% 
  as_tibble()
```


```{r}
extract_at_name <- function(text) {
  str_split(text, pattern = ' ') %>%
    unlist() %>%
    str_extract('@.*') %>%
    na.omit() %>%
    as_tibble()
}

tweets_washed <- tweets_washed %>% 
  mutate(at_name = purrr::map(content, ~extract_at_name(.x))) %>% 
  unnest(at_name)
```

```{r}
theme_set(theme_light())
map_data <- map_data('world')

tweets_washed %>% 
  filter(country == "United Arab")
ggplot() + 
  geom_polygon(map_data, mapping = aes(x = long, y = lat, group = group), fill = "white", color = 'gray60') + 
  geom_point(tweets_washed %>% drop_na(lat), 
             mapping = aes(x = long, y = lat, color = country, size = like_count/followers)) + 
  theme(
    legend.position = 'none'
  )
```
```{r}
tweets_washed %>% count(username, sort = T)
tweets_washed %>% 
  distinct(content,username, like_count, followers) %>% 
  group_by(username, followers) %>% 
  summarise(n = n(), like_count_pct = sum(like_count)/n) %>% 
  ggplot(aes(x = followers,y = like_count_pct, size = n, color = username)) + 
  geom_point() +
  theme(legend.position = 'none')
```

```{r}
tweets_washed %>% 
  count(platform, sort = T) %>% 
  ggpubr::ggbarplot(., x = 'platform', y = 'n', fill = 'platform', width = .5) + 
  geom_text(aes(label = n), vjust = -2) + 
  scale_y_continuous(expand = expansion(c(0,.2))) + 
  theme(
    axis.text.x = element_text(angle = 45,vjust = 1, hjust = 1)
  )

```


```{r}
tweets_washed %>% 
  distinct(content, username) %>% 
  count(username,sort = T) %>% 
  slice(1:5) %>% 
  ggpubr::ggbarplot(., x = 'username', y = 'n', fill = 'username', width = .5) + 
  geom_text(aes(label = n), vjust = -2) + 
  scale_y_continuous(expand = expansion(c(0,.2))) + 
  theme(
    axis.text.x = element_text(angle = 45,vjust = 1, hjust = 1),
    legend.position = 'none'
  )
```

```{r}
tweets_washed %>% 
  distinct(datetime, content, username) %>% 
  mutate(time = lubridate::as_date(datetime)) %>% 
  group_by(time) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x = time)) + geom_histogram(bins = 8)
```


