---
title: "mario_cart"
author: "shao"
date: "5/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
tuesdata <- tidytuesdayR::tt_load(2021, week = 22)
drives <- tuesdata$drivers
records <- tuesdata$records
```

How did the world records develop over time?
```{r}
library(tidyverse)

records %>% 
  ggplot(aes(x = date, y = time, colour = track)) + 
  geom_line() + 
  facet_wrap(~type + shortcut, scales = 'free')


```

Which track is the fastest?
```{r}
records %>% 
  group_by(track, type, shortcut) %>% 
  slice_tail(n = 1) %>% 
  arrange(time)
  
```

For which track did the world record improve the most?
```{r}
records %>% 
  group_by(track, type, shortcut) %>% 
  summarise(min = min(time), max = max(time)) %>% 
  mutate(improvement = max-min) %>% 
  arrange(desc(improvement))
```

For how many tracks have shortcuts been discovered?
```{r}
records %>% 
  filter(shortcut == 'Yes') %>% 
  distinct(track)
```

When were shortcuts discovered?

```{r}
records %>% 
  filter(shortcut == 'Yes') %>% 
  group_by(track) %>% 
  slice_head(n = 1) %>% 
  select(track, date) %>% 
  arrange(desc(date)) 
```

On which track does the shortcut save the most time?

```{r}
records %>% 
  filter(type == "Three Lap") %>% 
  select(track, type, shortcut,date,time) %>% 
  group_by(track, type, shortcut) %>% 
  slice_tail(n = 1) %>% 
  select(-date)%>% 
  spread(key = "shortcut", value = "time") %>% 
  na.omit() %>% 
  mutate(save = No - Yes) %>% 
  arrange(desc(save))
```

Which is the longest standing world record?
```{r}
records %>% 
  group_by(track, type, shortcut) %>% 
  arrange(track, type, shortcut,date) %>% 
  mutate(duration = lead(date) - date) %>% 
  arrange(desc(duration))
```

Who is the player with the most world records?
```{r}
records %>% 
  count(player, sort = TRUE) %>% 
  head(10) %>% 
  ggplot(aes(x = fct_reorder(player, n, .desc = T), y = n, fill = fct_reorder(player, n, .desc = T))) + 
  geom_bar(stat = 'identity', show.legend = F, width = .7, alpha = .7) +
  ggsci::scale_fill_npg() + 
  scale_y_continuous(expand = expansion(c(0,.1)))
```

Who are recent players?

```{r}
records %>% 
  arrange(desc(date)) %>% 
  filter(date >= "2021-01-01") %>% 
  count(player, sort = T) %>% 
  ggplot(aes(x = fct_reorder(player, n, .desc = T), y = n, fill = fct_reorder(player, n, .desc = T))) + 
  geom_bar(stat = 'identity', show.legend = F, width = .7, alpha = .7) +
  ggsci::scale_fill_npg() + 
  scale_y_continuous(expand = expansion(c(0,.1)))
  
```


